Evaluation of 3-point correlation functions from structural images on CPU and GPU architectures: accounting for anisotropy effects

### 2024-04-27 paper.tex
revision some chages part1

Input images must have appropriately high resolution for edge detection filter
to work correctly. A criterion for ``goodness'' of an image can be expressed
with $Q_\alpha$ parameter \cite{samarin2023robust}. Let $\alpha \in [0, 1]$
and $f(x)$ be (band-limited) input image ($x \in \mathbb{R}^2$ or
$\mathbb{R}^3$). We define $Q_\alpha$ as follows:
\begin{equation}
  \begin{aligned}
    f_0(x) &= f(x) - \langle f(x) \rangle \\
    Q_\alpha &= \frac{\int_{-\alpha\omega}^{\alpha\omega} |\hat{f_0}(z)|^2
      dz}{\int_{-\omega}^{\omega} |\hat{f_0}(z)|^2 dz}
  \end{aligned}
\end{equation}
where $\hat{f_0}$ is a Fourier transform of $f_0$ and $\omega$ is a folding
frequency which depends only on resolution of the image. If a criterion
$Q_{0.5} > 0.97$ holds then the image is suitable for application of
aforementioned algorithms for calculation of surface functions, otherwise
image's resolution can be improved with the help of interpolation prior to
computations \cite{samarin2023robust}.

@@

To estimate the error introduced by rotation, consider a two-phase medium
\cref{fig:roterror-noise} whose void phase is defined by an inequality
$f(x, y, z) > U$ where $f$ is a value noise function
\cite[Section IV.B]{samarin2023robust} and $U$ is a threshold. We produce images
of the noise rotated around $Z$ axis by $\theta$ radians by discretizing an
inequation $f(p(x'), p(y'), p(z')) > U$ where
\begin{equation*}
  \begin{aligned}
    x' &= x \cos \theta + y \sin \theta \\
    y' &= y \cos \theta - x \sin \theta \\
    z' &= z
  \end{aligned}
\end{equation*}
and
\begin{equation*}
  \begin{aligned}
    p(x) &= \left\{
    \begin{array}{ll}
      x'     & \quad x' < 1 \\
      2 - x' & \quad \text{otherwise}
    \end{array}
    \right. \\
    x ' &= x \mod 2
  \end{aligned}
\end{equation*}
Therefore we assume the noise to be periodic with the period equal to $2$ and
the interface between phases is continuous. Discretizing this noise for
different values of $\theta \in [0, \pi/4]$ with two different resolutions we
obtain the first dataset which contains the best possible discretization of the
rotated noise at those resolutions. For this study we have produced images with
dimensionality $300 \times 300 \times 300$ and $600 \times 600 \times 600$
voxels (i.e. the second resolution is twice as much as the first).

>>>>

Input images must have appropriately high resolution for edge detection filter
to work correctly. A criterion for ``goodness'' of an image can be expressed
with $Q_\alpha$ parameter \cite{samarin2023robust}. Let $\alpha \in [0, 1]$
and $f(x)$ be (band-limited) input image ($x \in \mathbb{R}^2$ or
$\mathbb{R}^3$). We define $Q_\alpha$ as follows:
\begin{equation}
  \begin{aligned}
    f_0(x) &= f(x) - \langle f(x) \rangle \\
    Q_\alpha &= \frac{\int_{-\alpha\omega}^{\alpha\omega} |\hat{f_0}(z)|^2
      dz}{\int_{-\omega}^{\omega} |\hat{f_0}(z)|^2 dz}
  \end{aligned}
\end{equation}
where $\hat{f_0}$ is a Fourier transform of $f_0$ and $\omega$ is a folding
frequency which depends only on resolution of the image. If a criterion
$Q_{0.5} > 0.97$ holds then the image is suitable for application of
aforementioned algorithms for calculation of surface functions, otherwise
image's resolution can be improved with the help of interpolation prior to
computations \cite{Samarin}.

@@

To estimate the error introduced by rotation, consider a two-phase medium
\cref{fig:roterror-noise} whose void phase is defined by an inequality
$f(x, y, z) > U$ where $f$ is a value noise function and $U$ is a threshold. We
produce images of the noise rotated around $Z$ axis by $\theta$ radians by
discretizing an inequation $f(p(x'), p(y'), p(z')) > U$ where
\begin{equation*}
  \begin{aligned}
    x' &= x \cos \theta + y \sin \theta \\
    y' &= y \cos \theta - x \sin \theta \\
    z' &= z
  \end{aligned}
\end{equation*}
and
\begin{equation*}
  \begin{aligned}
    p(x) &= \left\{
    \begin{array}{ll}
      x'     & \quad x' < 1 \\
      2 - x' & \quad \text{otherwise}
    \end{array}
    \right. \\
    x ' &= x \mod 2
  \end{aligned}
\end{equation*}
Therefore we assume the noise to be periodic with the period equal to $2$ and
the interface between phases is continuous. Discretizing this noise for
different values of $\theta \in [0, \pi/4]$ with two different resolutions we
obtain the first dataset which contains the best possible discretization of the
rotated noise at those resolutions. For this study we have produced images with
dimensionality $300 \times 300 \times 300$ and $600 \times 600 \times 600$
voxels (i.e. the second resolution is twice as much as the first).
